\chapter{Analysis of Existing Solutions and Technologies}

\section{Overview of Inventory Management Systems}

Inventory management systems are widely used in various industries, including healthcare, retail, and logistics. These systems are designed to track goods, monitor stock levels, and manage the flow of products.

In the healthcare sector, inventory management is especially critical due to the need for accurate tracking of medical equipment and consumables. Errors in inventory can lead to serious consequences, including delays in treatment and financial losses.

\section{Analysis of Existing Solutions}

There are many existing inventory management systems available on the market. Some of the most popular include enterprise resource planning (ERP) systems and specialized inventory tools.

However, many of these systems have limitations:
\begin{itemize}
    \item High cost of implementation and maintenance;
    \item Limited customization options;
    \item Lack of cross-platform support;
    \item Complexity of use for small and medium businesses.
\end{itemize}

\section{Cross-Platform Technologies}

Modern software development increasingly focuses on cross-platform solutions. These allow applications to run on multiple platforms such as Windows, web browsers, and mobile devices.

Popular technologies include:
\begin{itemize}
    \item Web technologies (HTML, CSS, JavaScript);
    \item Desktop frameworks (Electron, .NET);
    \item Mobile development platforms (Android SDK, Flutter).
\end{itemize}

Cross-platform development reduces development time and ensures consistency across devices.

\section{Problem Statement}

Based on the analysis, it can be concluded that existing solutions do not fully meet the needs of small and medium-sized medical businesses.

There is a need for a system that:
\begin{itemize}
    \item Is affordable and easy to use;
    \item Supports multiple platforms;
    \item Provides real-time data access;
    \item Can be adapted to specific business needs.
\end{itemize}

\section{Conclusion}

The analysis shows that there is a clear need for a modern, flexible, and cross-platform inventory management system. This justifies the development of the ENDOTECH system, which is described in the following chapters.