\chapter{System Implementation and Development}

This chapter presents the implementation of the ENDOTECH system, a cross-platform inventory and sales management solution for medical equipment.

\section{Project Structure and Technologies}

The system is implemented using Flutter and Firebase.

The application is structured as follows:

\begin{itemize}
    \item \texttt{lib/} – contains main application logic (screens, models, providers, services);
    \item \texttt{main.dart} – entry point of the application;
    \item Firebase initialization using \texttt{Firebase.initializeApp()};
\end{itemize}

State management is handled using the Provider package, including:

\begin{itemize}
    \item AuthProvider;
    \item InventoryProvider;
    \item SalesProvider;
\end{itemize}

\section{System Architecture Overview}

The system follows a client-server architecture, where Flutter acts as a client and Firebase as a backend.

\begin{itemize}
    \item Client – UI, logic, state management;
    \item Backend – authentication, database, synchronization.
\end{itemize}

\section{Authentication Module}

Authentication is implemented using Firebase Authentication.

\begin{lstlisting}[language=Dart]
FirebaseAuth.instance.signInWithEmailAndPassword(...)
\end{lstlisting}

The authenticated user ID is used to link sales data to users.

\section{Inventory Management Module}

Inventory is stored in Firestore collection \texttt{inventory}.

Each item includes:
\begin{itemize}
    \item name;
    \item quantity;
    \item price;
    \item timestamps.
\end{itemize}

Real-time streams are used to update UI automatically.

\section{Sales Processing Module}

Sales processing includes:

\begin{enumerate}
    \item checking available quantity;
    \item updating inventory;
    \item saving sale to database.
\end{enumerate}

\section{Testing and Validation}

The system was tested using:

\begin{itemize}
    \item manual testing;
    \item unit testing;
    \item real device testing.
\end{itemize}

\section{Challenges and Solutions}

\begin{itemize}
    \item Sync delays → optimized queries;
    \item Data consistency → centralized DB;
    \item Security → Firebase rules.
\end{itemize}

\section{Conclusion}

The implementation demonstrates a scalable and efficient system for inventory management using modern technologies.