\unchapter{Introduction}

\textbf{Topicality of the problem:}  

In recent years, the rapid development of information technologies has significantly transformed the healthcare sector. Medical institutions increasingly rely on digital systems to manage equipment, consumables, and operational processes. However, many clinics still use outdated or manual inventory management methods, which leads to inefficiencies, data inconsistencies, and financial losses.

The need for a modern, automated, and cross-platform system for managing medical equipment and sales processes is therefore highly relevant. Such a system can improve accuracy, optimize workflows, and provide real-time access to critical information.

\textbf{Aim of the study:}  

The aim of this thesis is to design and develop a cross-platform inventory and sales management system (ENDOTECH) for medical equipment and consumables.

\textbf{Object of the study:}  

The object of the study is information systems used in inventory and sales management within the healthcare sector.

\textbf{Subject of the study:}  

The subject of the study is the architecture, design, and implementation of a cross-platform system for managing medical equipment inventory and sales processes.

\textbf{Research problem:}  

The main problem addressed in this study is the lack of efficient, flexible, and scalable inventory management solutions tailored to the specific needs of medical equipment businesses, especially those requiring multi-platform accessibility (desktop, web, and mobile).

\textbf{Tasks of the study:}  

To achieve the aim of the thesis, the following tasks are defined:
\begin{enumerate}
    \item To analyze existing inventory and sales management systems;
    \item To study modern technologies and approaches for cross-platform development;
    \item To design the architecture of the ENDOTECH system;
    \item To implement the system for Windows, Web, and Android platforms;
    \item To test and evaluate the performance and usability of the system.
\end{enumerate}

\textbf{Hypothesis:}  

The implementation of a cross-platform inventory and sales management system will improve operational efficiency, reduce errors, and enhance decision-making processes in medical equipment management.

\textbf{Research methods:}  

The following research methods are used in this thesis: analysis of scientific literature, comparative analysis of existing systems, system design and modelling, software development, and practical testing of the implemented solution.

\textbf{Approbation of the study:}  

The developed system has been implemented in a real company environment, where it is currently used for managing inventory and sales of medical equipment, demonstrating its practical effectiveness and applicability.
