\chapter{System Architecture and Design}

\section{Overview of the System}

The ENDOTECH system is designed as a cross-platform mobile solution for managing inventory and sales of medical equipment. The system is implemented using Flutter for the user interface and Firebase as the backend platform.

This approach ensures scalability, real-time data synchronization, and accessibility across different devices.

\section{System Architecture}

The system follows a client-server architecture. The Flutter application acts as a client, while Firebase provides backend services.

The architecture consists of the following components:

\begin{itemize}
    \item User Interface Layer – responsible for user interaction and data visualization;
    \item Application Layer – handles business logic and state management using the Provider package;
    \item Backend Layer – implemented using Firebase services such as Authentication and Cloud Firestore.
\end{itemize}

This architecture allows the system to be modular, scalable, and easy to maintain.

\section{Technology Selection}

The ENDOTECH system is implemented using modern technologies that support cross-platform development and real-time data processing.

The main technologies include:

\begin{itemize}
    \item Flutter – for building cross-platform mobile applications;
    \item Dart programming language – for implementing application logic;
    \item Firebase Authentication – for user authentication and access control;
    \item Cloud Firestore – for real-time NoSQL database management;
    \item Provider – for state management and separation of concerns.
\end{itemize}

This technology stack was selected because it enables rapid development, reduces maintenance costs, and provides seamless integration between frontend and backend.

Compared to native development, Flutter allows the use of a single codebase for multiple platforms, significantly reducing development time.

Cloud Firestore was chosen instead of a relational database due to its flexible document-based structure, real-time data synchronization, and support for offline functionality.

\section{System Functionality}

The system provides the following main features:

\begin{itemize}
    \item Inventory management (adding, editing, deleting products);
    \item Sales tracking and transaction management;
    \item Real-time stock monitoring;
    \item User authentication and role-based access control;
    \item Synchronization of data across devices.
\end{itemize}

\section{Data Flow and Interaction}

The system operates using real-time communication between the client application and the Firebase backend.

User actions in the Flutter application trigger database operations in Cloud Firestore. Changes in the database are immediately reflected in the user interface through real-time listeners.

This ensures data consistency and up-to-date information across all devices.

\section{Conclusion}

The designed system architecture provides a robust foundation for the ENDOTECH system. The use of Flutter and Firebase ensures scalability, flexibility, and efficient data management, making the system suitable for real-world medical equipment inventory management.